---
title: "Statistical Concepts"
---

This section will talk about statistical concepts, which are the basics in statistical and casual inference.

For the following assignments the table *"random_vars.rds"* is used.
```{r}
#| echo: false
library(tidyverse)
random_vars <- readRDS("~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/random_vars.rds")
sorted_vars_age <- arrange(random_vars,age)
sorted_vars_age
```

# Compute statistical values
## Compute statistical values for age

### expected value

````{r}
groupedAge <- sorted_vars_age %>% group_by(age) %>% summarise( n = n())
expectedAge <- weighted.mean(groupedAge[,1],groupedAge[,2])
expectedAge
````

### variance
````{r}
varianceAge <- var(groupedAge[[1]])
varianceAge
````

### standard deviation
````{r}
deviationAge <- sd(groupedAge[[1]])
deviationAge
````

## Compute statistical values for income

### expected value

````{r}
groupedIncome <- sorted_vars_age %>% group_by(income) %>% summarise( n = n())
expectedIncome <- weighted.mean(groupedIncome[,1],groupedIncome[,2])
expectedIncome
````

### variance

````{r}
varianceIncome <- var(groupedIncome[[1]])
varianceIncome
````

### standard deviation
````{r}
deviationIncome <- sd(groupedIncome[[1]])
deviationIncome
````

# Explain the usefullness of comparing the standard deviations

It doesn't make sense to compare the two standard deviations as they describe
the variation of two different data sets, what would make more sense is to
compare the standard deviations of the income of different age groups
 
# Examine the relationship between both variables

## Covariance

````{r}
#| echo: false
covariance <- cov(sorted_vars_age[[1]],sorted_vars_age[[2]])
covariance
````

## Correlation

````{r}
#| echo: false
correlation <- cor(sorted_vars_age[[1]],sorted_vars_age[[2]])
correlation
````

# Interpret the results

The correlation is easier to interpret, as it is normalized in respect to the
variance of the two data sets.
From the fundamentals we learned that a high covariance means a low independence,
however because of the scaling of the data sets we can't define what high means.
 
Here comes the correlation into play as it norms the covariance to a value of
-1 to 1, where values close to 1 mean a nearly linear relationship.
In our data set we have a correlation of 0.548, which indicates that there exists
a dependency between age and income and that with growing age the income also growths.
However as 0.548 is still far away from 1 we can also conclude that there are many 
more factors, which have an impact on the income, which we didn't consider.

# Compute the conditional expected value

````{r}
# age < 18
selectedAgeOne <- sorted_vars_age  %>% filter(age<18) %>% group_by(income) %>% summarise( n = n())
conAgeOne <- weighted.mean(selectedAgeOne[,1],selectedAgeOne[,2])
conAgeOne
# age [18,65)
selectedAgeTwo <- sorted_vars_age  %>% filter(age>=18 & age<65) %>% group_by(income) %>% summarise( n = n())
conAgeTwo <- weighted.mean(selectedAgeTwo[,1],selectedAgeTwo[,2])
conAgeTwo
# age >= 65
selectedAgeThree <- sorted_vars_age  %>% filter(age>=65) %>% group_by(income) %>% summarise( n = n())
conAgeThree <- weighted.mean(selectedAgeThree[,1],selectedAgeThree[,2])
conAgeThree
````

This three values express the expected value for the given age groups, as one can see the value for the age group of 18 - 65 is the highest, as this is the age group, who normally works and actively earns money.
