---
title: "Directed Acyclic Graphs"
---

This section will introduce an option to graphically represent the relationship between 
different variables with the help of **directed acylic graphs (DAGs)**

# Display parking spot example

````{r}
#| echo: false
library(dagitty)
library(ggdag)
library(ggplot2)

parking_spot <- 'dag{
bb="0,0,1,1"
spots [exposure,pos="0.3,0.4"]
sales [outcome,pos="0.4,0.4"]
location [pos="0.35,0.5"]
spots -> sales
location -> sales
location -> spots
}
'

ggdag_status(parking_spot) +
  guides(fill = "none", color = "none")+
  theme_dag()+
  geom_dag_text(color = "black")
````

As one can see the location influences the number of available spots and sales, while spots also influences the sales

# Computing relevant values of data set *costumer_sat.rds*

````{r}
#| echo: false

df <- readRDS("~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/customer_sat.rds")
df

````

## Regress *satisfaction* on *follow_ups*

````{r}
#| echo: false

lm_followUp <- lm(satisfaction ~ follow_ups, data = df)
summary(lm_followUp)
````

## Regress *satisfaction* on *follow_ups* and account for *subscription*

`````{r}
#| echo: false
lm_follAndSub <- lm(satisfaction ~ follow_ups + subscription, data = df)
summary (lm_follAndSub)
````

# Compare the coefficients

**Satisfaction on follow_ups**

m1 = -3.3093 b = 78.886

**Satisfaction on follow_ups and account for subscription**

m1 = 2.1944 m2 = 44.7222 m3 = 18.0722 b = 26.7667

Explanation: As the satisfaction decreases, if the data is not conditioned 
on subscription, but at the same time increases, if conditioned on subscription
you can assume that the subscription has an negative impact on the satisfaction
This can have multiple explanations, maybe the product is to expensive or
the amount of functions to overwhelming.

# Plot data

````{r}
#| echo: false

# Not conditioning on subscription
simps_not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

# Conditioning on subscription
simps_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

# Plot both plots
simps_not_cond
simps_cond
````

As one can see that if the subscription is accounted for, the satisfaction increases for all subscription tiers if the support does a follow up.
