---
title: "Randomized Controlled Trials"
---

This section will use the data from *abtest_online.rds*
````{r}
#| echo: false

library(ggplot2)

#load dataset
df <- readRDS('~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/abtest_online.rds')
summary(df)
````

# Check the balance of the covariates

````{r}
#| echo: false

#visit (independent)
compare_visit <- 
  ggplot(df, 
         aes(x = chatbot, 
             y = previous_visit, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "previous visits", title = "Difference in previous visits")

# mobile (independent)
compare_mobile <- 
  ggplot(df, 
         aes(x = chatbot, 
             y = mobile_device, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "mobile device", title = "Difference in mobile device")

# outcome (dependent)
compare_purchase <- 
  ggplot(df, 
         aes(x = chatbot, 
             y = purchase, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "purchase", title = "Difference in purchase")

compare_amount <- 
  ggplot(df, 
         aes(x = chatbot, 
             y = purchase_amount, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "Purchase amount", title = "Difference in purchase amout")

# Plot 
compare_visit
compare_mobile
#compare_purchase
#compare_amount

````
The plot shows the distribution of the two groups *chatbot* and *no chatbot*.
As one can see the covariate of previous_visits is not balanced, while the covariate for mobile_device is balanced.

# Regression to find the effect of chatbot on sales

````{r}
#| echo: false

lm_ate <- lm(purchase_amount ~ chatbot, data = df)
summary(lm_ate)

lm_ate_visit <- lm(purchase_amount ~ chatbot + previous_visit, data = df)
summary(lm_ate_visit)

````

Regression confirms the results of part 1. As the previous visits are not a 
balanced covariate. They can't be excluded from the regression

# Subgroup specific effects

This journal used for this assignment the subgroup: *moblie users*.

````{r}
#| echo: false

lm_cate <-lm(purchase_amount ~ chatbot*mobile_device + previous_visit, data = df)
summary(lm_cate)
````

The subgroup of mobile users has no specific effect on the purchase amount,
as one can see by the results of the CATE with mobile users, as they are not significant.

# Logistic regression for *purchase*

````{r}
#| echo: false
glm_ate <- glm(purchase ~ chatbot + previous_visit, family=binomial(link='logit'), data = df)
summary(glm_ate)
````

e^(-0.96827)^ = 0.3797 -> 1 - 0.3797 = 0.6203

The chatbot is associated with a 62% reduction of purchases. This means
that chatbot more than halves the amount of purchases made.
