---
title: "Difference-in-Differences"
---

In this section the following data will be used:
````{r}
#| echo: false

library(tidyverse)
library(ggplot2)

# load dataset

df <- readRDS('~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/hospdd.rds')
df
````

# Manually computing the mean satisfaction

## Treated hosptials

**BEFORE**
````{r}
# get ID of treated hospitals
treated_id <- df %>% filter( procedure == 1) %>% pull(hospital)
treated_id <- unique(treated_id)

# calculate mean satisfaction before for treated hospitals
treated_before <- c()

for(i in treated_id){
  x <- df %>% filter(hospital == treated_id[i],month<4) %>% pull (satis)
  treated_before <- c(treated_before,x)
}

treated_before <- mean(treated_before)
treated_before
````

**AFTER**
````{r}
# calculate mean satisfactions after for treated hospitals
treated_after <- c()

for(i in treated_id){
  x <- df %>% filter(hospital == treated_id[i],month>=4) %>% pull (satis)
  treated_after <- c(treated_after,x)
}

treated_after <- mean(treated_after)
treated_after
````

## Control hospitals

**BEFORE**
````{r}
# get ID of control hospitals
control_id <- df %>% filter( procedure == 0, month == 4) %>% pull(hospital)
control_id <- unique(control_id)

# calculate mean satisfaction before for control hospitals
control_before <- c()

for(i in control_id){
  x <- df %>% filter(hospital == control_id[i],month<4) %>% pull (satis)
  control_before <- c(control_before,x)
}

control_before <- mean(control_before)
control_before
````

**AFTER**
`````{r}
# calculate mean satisfactions after for control hospitals
control_after <- c()

for(i in control_id){
  x <- df %>% filter(hospital == control_id[i],month>=4) %>% pull (satis)
  control_after <- c(control_after,x)
}

control_after <- mean(control_after)
control_after
````

## Conclusion

One can see that the treated hospitals have an higher mean satisfaction
after the treatment, while the mean satisfaction of the control hospitals
stayed nearly the same. This indicates that the treatment is successful.

# Linear regression to compute the estimate

One wants to include them as as.factor(), as this ensures that they will be
treated as categorical variables and not as continuous.
Which wouldn't make sense for months or ID's.

````{r}
#| echo: false

# get month of after treatment

summary(lm(satis ~ as.factor(procedure)*month + as.factor(month) + as.factor(hospital) , data = df))
````

If one looks at the results of the lm and the coefficients, it can be seen that 
the procedure*month coefficient, which represents the average treatment effect
is really small and not significant for the model, while regressors like the 
hospital have an big significance.