---
title: "Instrumental Variables"
---

This section will introduce the instrumental variables and uses the following
data for this:

````{r}
#| echo: false

library(tidyverse)
library(dagitty)
library(ggdag)
library(ggplot2)
library(estimatr)

df <- readRDS('~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/rand_enc.rds')
df
````

# *DAG* of data

````{r}
#| echo: false

# create DAG from dagitty
dag_model <- 'dag {
bb="0,0,1,1"
"new feature" [exposure,pos="0.075,0.4"]
"time spent" [outcome,pos="0.4,0.4"]
"random encounter"[pos="0.2,0.5"]
"new feature" -> "time spent"
"random encounter" -> "new feature"
}
'
# draw DAG
ggdag_status(dag_model) +
  guides(fill = "none", color = "none")+
  theme_dag()+
  geom_dag_text(color = "black")
````

The random encounter has a influence on the user to use the new feature.
However, it has no influence on the time spent in the app, as it is
not mandatory to use the feature.

# Naive model

````{r}
#| echo: false

model_naive <- lm(time_spent ~ used_ftr, data = df)
summary(model_naive)
````

If we compute the naive, biased estimate, which assumes there are no other
influences, besides the new feature, regarding time spent we get an estimation
from 10.82269, which would indicate that the new feature is a huge succes

# Testable assumptions

## Monotonicity assumption

The monotonicity assumption is fulfilled, as there exists no defiers.
This means that the effect of the instrument goes in the same/correct direction.
For a plot of this behaviour look at the DAG from part 1.

## Instrumentent Relevance

````{r}
#| echo: false
first_stage <- lm(used_ftr~rand_enc, data = df)
summary(first_stage)
````

The linear regression from rand_enc to used_ftr, shows 
that the random encounter is statistically significant. As can be observe by the p-value and F-statistic.

## Exclusion restriction

Assumption is not testable

## Independent assumption

````{r}
#| echo: false

# Predicted 'probabilities' from first stage
pred_fs <- predict(first_stage)

# Create table with predictions and actual decisions
pred_vs_actl <- tibble(
  pred = pred_fs,
  actl = df$used_ftr
)

# Plot predictions vs original
ggplot(pred_vs_actl, aes(x = pred, y = actl, color = as.factor(actl))) +
  geom_jitter(alpha = .5) +
  scale_color_discrete(labels = c("Control Group", "Treatment Group")) +
  theme(legend.title = element_blank())
````

From the plot we can see that the predicted probabilities are completely
overlapping between actually using the new feature and getting the randomized
encouragement.

## Adequate procedure

Furthermore we can assume that there is no confounding between the instrument
and the treatment, as the people are chosen randomly. Furthermore there is no
confounding between the instrument and the outcome as we can assume, that
people don't change their user behavior based on a start message. Look at the
DAG for clarification.
Therefore the independence assumption is fulfilled.

The last assumption the "stable unit treatment value assumption" is also
fulfilled as another user receiving a start message, should have no influence
on your own outcome.

Therefore one can assume that the instrumental variable estimation is an
adequate procedure. As all assumptions are fulfilled and therefore is the 
variable valid.

# Compute the IV estimate using 2SLS

````{r}
#| echo: false

model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc , data = df)
summary(model_iv)
````

One can see that the estimation for the coefficient "used-feature" got smaller.
This points to a bias as the difference is relatively big with ~1.0.
As the naive, biased estimation is bigger than the actual estimation, we have
an upward bias.
