---
title: "Regression Discontinuity"
---

In this section there will be used two datasets. The first part uses the *coupon.rds*
data:
````{r}
#| echo: false
library(tidyverse)
library(ggplot2)
library(rddensity)
library(ggthemr)


###################################### Coupons ###############################

# load data

df <- readRDS('~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/coupon.rds')
df
````

# Bandwidth calculation

## Half the bandwidth

````{r}
#| echo: false

c0 <- 60
bwh <- c0 +c(-2.5,2.5)

# Subsets below and above threshold in specified bandwidth
df_bw_below <- df %>% filter(days_since_last >= bwh[1] & days_since_last < c0)
df_bw_above <- df %>% filter(days_since_last >= c0 & days_since_last <= bwh[2])

df_bw <- bind_rows(df_bw_above, df_bw_below)

# Extract values for vertical lines to visualize local average treatment effect
model_bw_below <- lm(purchase_after ~ days_since_last, df_bw_below)
model_bw_above <- lm(purchase_after ~ days_since_last, df_bw_above)

y0 <- predict(model_bw_below, tibble(days_since_last = c0))
y1 <- predict(model_bw_above, tibble(days_since_last = c0))

late <- y1 - y0
sprintf("LATE: %.2f", late)

# Compute coefficients for specified bandwidth.
lm_bw <- lm(purchase_after ~ days_since_last_centered + coupon, df_bw)
summary(lm_bw)
````

## Double the bandwidth

````{r}
#| echo: false
# Specify bandwidth
bwd <- c0 +c(-10,10)

# Subsets below and above threshold in specified bandwidth
df_bw_below <- df %>% filter(days_since_last >= bwd[1] & days_since_last < c0)
df_bw_above <- df %>% filter(days_since_last >= c0 & days_since_last <= bwd[2])

df_bw <- bind_rows(df_bw_above, df_bw_below)

# Extract values for vertical lines to visualize local average treatment effect
model_bw_below <- lm(purchase_after ~ days_since_last, df_bw_below)
model_bw_above <- lm(purchase_after ~ days_since_last, df_bw_above)

y0 <- predict(model_bw_below, tibble(days_since_last = c0))
y1 <- predict(model_bw_above, tibble(days_since_last = c0))

late <- y1 - y0
sprintf("LATE: %.2f", late)

# Compute coefficients for specified bandwidth.
lm_bw <- lm(purchase_after ~ days_since_last_centered + coupon, df_bw)
summary(lm_bw)
````

## Results

The results seem to be relative sensitive to changing the bandwidth if you want
to get the exact value of the LATE, however the variable days_since_last_centered
lost its significance, therefore you can notice if you have the wrong bandwidth.

# Running Variable

The second dataset, which is used is *shipping.rds*:
````{r}
#| echo: false

df <- readRDS("~/GitHub/cdsba-KonsGo/Causal_Data_Science_Data/shipping.rds")
df
````

Just from the info alone, one can assume that the purchase amount is continuous
and smooth. Therefore it should be a valid running variable.
However if the value is known at which free shipping is offered, which normally
is the case, one can expect a heaping at the cut-off. Then this is the case,
the continuity assumption is no longer fulfilled, as the function is not smooth.
 
In contrast to the coupon, and the day since last purchase, which people can't
manipulate. The purchase amount can be manipulated by the customer.

For that reason I would argue that the purchase amount for free shipping is not a 
valid running variable, as it can be manipulated by the customer and as a result,
one would notice a heaping at the cut-off.

````{r}
#| echo: false

ggthemr('flat dark')
# Manual plot
ggplot(df, aes(x = purchase_amount)) +
  geom_histogram(binwidth = 5, color = "white", boundary = 30, alpha = .6) +
  geom_vline(xintercept = 30, color = ggthemr::swatch()[5]) +
  xlab("Purchase amount")+
  ylab("Number of purchases")
````

As expected one can see that the number of purchases is falling of sharply right
before the 30 mark, which grants free shipping.
This can be explained by the fact that the free shipping purchase amount is known
before hand and customers are more willing to buy another small thing to get
past that cut-off.

Therefore this plot nicely illustrates that the purchases amount is not a suitable
running variable, as the continuity assumption is not fulfilled.